Usage metrics

### 2020-12-11 inst/analysis/usage_metrics.Rmd
Adding ratio of call sites triggered over the total number of them in the corpus

---
title: "Usage metrics"
author: "Pierre Donat-Bouillud"
output:
    html_document:
        gallery: false
        toc: true
        toc_depth: 3
        toc_float: true
        df_print: paged
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  base_dir: /var/lib/R/project-evalR
  calls_packages_path: /run/package-evals-traced.9/summarized-packages.fst
  corpus_path: /run/package-evals-traced.9/corpus.fst
---

@@

jan <- TRUE

@@

base_dir <- params$base_dir
# Set the paths, and customize for Jan.
if (jan) {
  base_dir <- "/mnt/code/eval"
}
eval_calls_path <- paste0(base_dir, params$calls_packages_path)
corpus_path <- paste0(base_dir, params$corpus_path)
```

@@

```{r read}
read_fst(eval_calls_path) %>% as_tibble() -> E_raw
read_fst(corpus_path) %>% as_tibble() -> C_raw
```

The two data sets are E and C for conciseness.  C is only used here to compute
the corpus size. E is used throughout. Recall that E_raw has the source data
with all columns.

@@

>>>>

---
title: "Usage metrics"
author: "Pierre Donat-Bouillud"
output:
    html_document:
        gallery: false
        toc: true
        toc_depth: 3
        toc_float: true
        df_print: paged
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  base_dir: /var/lib/R/project-evalR/run/package-evals-traced.10/
  calls_packages_path: summarized-packages.fst
  corpus_path: corpus.fst
  static_evals_path: package-evals-static.csv
---

@@

jan <- FALSE

@@

base_dir <- params$base_dir
# Set the paths, and customize for Jan.
if (jan) {
  base_dir <- "/mnt/code/eval"
}
eval_calls_path <- paste0(base_dir, params$calls_packages_path)
corpus_path <- paste0(base_dir, params$corpus_path)
eval_static_path <- paste0(base_dir, params$static_evals_path)
```

@@

```{r read}
read_fst(eval_calls_path) %>% as_tibble() -> E_raw
read_fst(corpus_path) %>% as_tibble() -> C_raw

read_csv(eval_static_path) %>% semi_join(C_raw, by = "package") -> E_static
```

The two data sets are E and C for conciseness.  C is only used here to compute
the corpus size. E is used throughout. Recall that E_raw has the source data
with all columns. E_static corresponds to static information about the call sites.

@@

How many call sites and how many packages did we exercise out of the total number of call sites of the corpus?

```{r exercised-call-sites}
nb_static_call_sites <- nrow(E_static)

static_call_sites_per_package <- E_static %>%
  count(package, sort = TRUE)

static_at_least_one_call_site <- static_call_sites_per_package %>%
  filter(n >= 1)

r("nb static call sites", nb_static_call_sites)
r("call sites percent", ratio(nb_ev_call_sites, nb_static_call_sites))
r("nb static at least one call site", nrow(static_at_least_one_call_site))
r("static at least one call site percent", ratio(nrow(packages_at_least_one_call_site), nrow(static_at_least_one_call_site)))
```
